GO Enrichment
-------------

###Read in YAML guide

```{r}
library(yaml)
yamls <- yaml.load_file("de.yml")
sample1 <- yamls$sample1
sample2 <- yamls$sample2

sample1
sample2
```

```{r}
library(goseq)
library(GO.db)
```

Setting up the DE table for GO analysis
-----------------

###File Input
Input the output from DE analysis.  This is made for a list that includes only the significant genes.  
?paste

```{r}
sigOnly <- read.table(paste(sample1,"_",sample2,"_DE_sig.txt", sep=""), header = TRUE, fill = TRUE)
head(sigOnly)
dim(sigOnly)
colnames(sigOnly)
colnames(sigOnly)[1] <- "itag" 
```

###Subset 
First I need to subset the list to up or down regulated, then add a new colum that specififys 1.  This column is need to for merging. 

```{r}
upITAG <- subset(sigOnly, logFC > 0, select = c(itag))
upITAG$up <- 1 
    
downITAG <- subset(sigOnly, logFC < 0, select = c(itag))
downITAG$down <- 1 
  
allITAG <- subset(sigOnly, select = c(itag))
allITAG$all <- 1
```

###Merge I - with normalized ITAG length gene list

read in guide. 
```{r}
geneLength <- read.csv("../normalized_genes_length.csv")
head(geneLength)
#isolate just the gene list
genes <- subset(geneLength, select = c(itag))
```

First merge each table to geneLength
```{r}
upITAGmerge <- merge(genes, upITAG, by = "itag", all= TRUE)
dim(upITAGmerge)
downITAGmerge <- merge(genes, downITAG, by = "itag", all= TRUE)
dim(downITAGmerge)
allITAGmerge <- merge(genes, allITAG, by = "itag", all= TRUE)
dim(allITAGmerge)
head(allITAGmerge)
```



###Merge II - Merge them all together.

```{r}
matrixGOupdown <- merge(upITAGmerge, downITAGmerge, by = "itag", all = TRUE)
head(matrixGOupdown)
matrixGOupdownall <- merge(matrixGOupdown, allITAG, by = "itag", all = TRUE)
head(matrixGOupdownall)
matrixGO <- merge(matrixGOupdownall, geneLength, by = "itag", all = TRUE)
head(matrixGO)
```

###Clean Up
```{r}
matrixGO[is.na(matrixGO)] <- 0
head(matrixGO)
```

This is if you want to write out the table. 
write.table(matrixGO, "mydata.txt", sep="\t", quote= FALSE)

GO enrichment
-----------------

The is the input of the GOslim categories.  There are only two columns 1. itag and 2. go

```{r}
pat <- matrixGO
head(pat)
cate <- read.table("../melted.GOTable.txt",header=TRUE)
head(cate)
```

###Subseting for GO analysis

Specify the column you are interested in `pat$all` refers to all the DE gene regardless if they are up or down regulated. If you want to specify down regulated, specify `pat$down`.

```{r}
genes = as.integer(pat$all)
names(genes) = pat$itag
table(genes)
length(genes)
```

The PWF is calculated by ﬁtting a monotonic spline to the binary data series of diﬀerential expression.  A monotonic spline is a specific type of cubic spline, which fits continuous functions through discrete data. Monotonicity preserves order between ordered sets. This is the point in which gene length is taken into account. 

The `nullp()` function is finding the null distribution... The nullp plots the fit of the null distribution to the data.  This is a quality control step and want to check the goodness of fit to the data. 

```{r}
pwf = nullp(genes,bias.data=pat$length)
```

```{r}
GO.wall = goseq(pwf,gene2cat = cate)
head(GO.wall)
```

Here is where you can specify the p-value cut-off

```{r}

enriched.GO = GO.wall$category[p.adjust(GO.wall$over_represented_pvalue, method = "BH") < 0.05]

enriched.GO

my.GO <- as.character(enriched.GO)
my.GO.table <- Term(my.GO)
my.GO.table
t <- as.matrix(my.GO.table)
```

write.table(t, file=paste(sample1,"_",sample2,"DE1_sigonly_down_GO.txt", sep=""))

