Making the table
-----------------

```{r}
sigOnly <- read.csv("tf2cmbr_wtcmbr_DE1_sigonly.csv")
head(sigOnly)
dim(sigOnly)
colnames(sigOnly)
```

###Subset 
First I need to subset the list to up or down regulated, then add a new colum that specififys 1.  This column is need to for merging. 

```{r}
upITAG <- subset(sigOnly, logFC < 0, select = c(ITAG))
upITAG$up <- 1 
    
downITAG <- subset(sigOnly, logFC > 0, select = c(ITAG))
downITAG$down <- 1 
  
allITAG <- subset(sigOnly, select = c(ITAG))
allITAG$all <- 1
```

###Merge I - with normalized ITAG length gene list

read in guide. 
```{r}
geneLength <- read.csv("normalized_genes_length.csv")
head(geneLength)
#isolate just the gene list
genes <- subset(geneLength, select = c(ITAG))
```

First merge each table to geneLength
```{r}
upITAGmerge <- merge(genes, upITAG, by = "ITAG", all= TRUE)
downITAGmerge <- merge(genes, downITAG, by = "ITAG", all= TRUE)
allITAGmerge <- merge(genes, allITAG, by = "ITAG", all= TRUE)
```

###Merge II - Merge them all together.

```{r}
head(matrixGO)
matrixGOupdown <- merge(upITAGmerge, downITAGmerge, by = "ITAG")
matrixGO <- merge(matrixGOupdown, allITAG, by = "ITAG")
```

###Clean Up
```{r}
matrixGO[is.na(matrixGO)] <- 0
head(matrixGO)
```

###Write File 

If you are working in one directory make sure you specify which is which. 

```{r}
write.csv(matrixGO, "matrixGO.csv", row.names=FALSE, na="")
```
