GO Enrichment
-------------

```{r}
library(goseq)
library(GO.db)
```

###File Input

This is the input of your go file, which needs to be properly formated. Need to incorporate into this scipt the proper formatting. 

```{r}
pat <- matrixGO#read.table("matrixGO.txt",header=TRUE)  #THESE ARE FUCKING IDENTICAL!!!!
str(pat)
str(matrixGO)
head(pat)

```

The is the input of the GOslim categories.  There are only two columns 1. itag and 2. go

```{r}
cate <- read.table("melted.GOSlim.txt",header=TRUE) 
head(cate)
```

###Subseting for GO analysis

Specify the column you are interested in `pat$all` refers to all the DE gene regardless if they are up or down regulated. If you want to specify down regulated, specify `pat$down`.

```{r}
genes = as.integer(pat$all)
names(genes) = pat$itag
table(genes)
length(genes)

pwf = nullp(genes,bias.data=pat$length)


GO.wall = goseq(pwf,gene2cat = cate)
head(GO.wall)
```

Here is where you can specify the p-value cut-off

```{r}
enriched.GO = GO.wall$category[p.adjust(GO.wall$over_represented_pvalue, method = "BH") < 0.05]

enriched.GO

my.GO <- as.character(enriched.GO)
my.GO.table <- Term(my.GO)
my.GO.table
t <- as.matrix(my.GO.table)
```

write.table(t, file="tf2cmbr_wtcmbr_DE1_sigonly_ALL_GOmerge.txt")


